INLA replication

### 2022-10-11 src/example_inla-replication/inla-replication.Rmd
A few small updates to this. Will need a big update later

1. Locate the mode of $\log p(\theta \, | \, y)$ which is the same as $\text{argmin}_{\theta} (-\log L^\star_f(\theta))$ and can be calculated as above.
2. Calculate negative Hessian at the mode.
The solution is likely to use some version of `h$env$spHess` although it's not clear which one.
3. Test points against the $\delta_z$ condition

@@

## Stage 3: get $\tilde p(x_i \, | \, \theta, y)$

@@

Obtain marginals of $\tilde p_G(x \, | \, \theta, y)$ from above.

@@

Compute the Laplace approximation

@@

\begin{equation}
  \tilde p(x_i \, | \, y) = 
  \sum_{k = 1}^K \tilde p(x_i \, | \, \theta^{(k)}, y) \times \tilde p(\theta^{(k)} \, | \, y) \times \Delta^{(k)}
\end{equation}

@@

Consider the following simple model for i.i.d. observations $y = (y_1, \ldots, y_n)$
\begin{align}
y_i \, | \, x, \theta &\sim \mathcal{N}(x, 1/\theta), \\
x &\sim \mathcal{N}(x_0 = -3, 1/\tau_0 = 4), \\
\theta &\sim \text{Gamma}(a = 1.6, b = 0.4).
\end{align}

@@

```{r, fig.height=2, fig.cap=""}
data.frame(index = 1:30, y = y) %>%
  ggplot(aes(x = index, y = y)) +
  geom_point(shape = 4) +
  geom_hline(yintercept = -3, col = "#666666", lty = "dashed") +
  theme_minimal()
```

>>>>

1. Locate the mode of $\log p(\theta \, | \, y)$ which is the same as $\text{argmin}_{\theta} (-\log L^\star_f(\theta))$ and can be calculated as above.
2. Calculate negative Hessian at the mode using e.g. `h$env$spHess`.
3. Reparameterise in terms of $z$ coordinates along the eigenvectors of the Hessian starting at the mode
3. Test points at a certain step-size ($\delta_z$) against a condition whereby they must have sufficient posterior density (using a parameter $\delta_{\pi}$)

For a more detailed run through of the grid integration method, see the [INLA two dimensional grid replication](https://athowes.github.io/elgm-inf/inla-grid.html) notebook.

@@

We could also use an adaptive Gauss Hermite quadrature rule.
See the [Implementing Approximate Bayesian Inference using
Adaptive Quadrature: the `aghq` Package](https://arxiv.org/pdf/2101.04468.pdf) paper.
## Stage 3: get $\tilde p(x_i \, | \, \theta, y)$

@@

Obtain marginals of $\tilde p_{\text{G}}(x \, | \, \theta, y)$ from above.

@@

Compute the Laplace approximation $\tilde p_{\text{LA}}(x_i \, | \, \theta, y)$.

@@

Combine the Laplace approximation to the hyperparameter posterior from Stage 1, the quadrature nodes and weights from Stage 2, and the chosen posterior latent field marginal approximation from Stage 3 together in one equation:
\begin{equation}
  \tilde p(x_i \, | \, y) = 
  \sum_{k = 1}^K \tilde p(x_i \, | \, \theta^{(k)}, y) \times \tilde p(\theta^{(k)} \, | \, y) \times \Delta^{(k)}
\end{equation}

@@

This is the example from the book [Spatial and Spatio-temporal Bayesian Models with `R-INLA`](https://onlinelibrary.wiley.com/doi/book/10.1002/9781118950203).
Consider the following simple model for i.i.d. observations $y = (y_1, \ldots, y_n)$
\begin{align}
y_i \, | \, x, \theta &\sim \mathcal{N}(x, 1/\theta), \\
x &\sim \mathcal{N}(x_0 = -3, 1/\tau_0 = 4), \\
\theta &\sim \text{Gamma}(a = 1.6, b = 0.4).
\end{align}

@@

```{r, fig.height=2, fig.cap=""}
data.frame(index = 1:30, y = y) %>%
  ggplot(aes(x = index, y = y)) +
  geom_point() +
  geom_hline(yintercept = -3, col = "#666666", lty = "dashed") +
  theme_minimal()
```
